HPC final project: \\ Ewald summation on stokes potential

### 2019-05-21 report/slides.tex
Update the slides

\begin{frame}{Compute $u^F$ by FFT}
\begin{equation}
\mathbf{u}^F (\mathbf{x}_m) = \frac{1}{V} \sum_{\mathbf{k} \neq 0} \mathbf{B}(\xi, \mathbf{k}) e^{-k^2/4\xi^2} \left(\sum_{n=1}^{N} \mathbf{f}_n e ^{i \mathbf{k} \cdot \mathbf{x}_n} \right)e ^{-i \mathbf{k} \cdot \mathbf{x}_m}
\end{equation}
is the combination of two steps of NuFFT (Non-uniform FFT).

\textbf{Can be done efficiently by Gaussian Gridding \& FFT!}
\begin{itemize}
	\item \textbf{Gaussian Gridding}: \\
	Compute $ \sum_{n=1}^N \mathbf{f}_n e^{-2 \xi^2 |\mathbf{x} - \mathbf{x}_n|_{\ast}^2 / \eta}$ \\
	Can be accelerated with Greengard's trick \cite{Greengard2004} and  OpenMP!
	\item \textbf{FFT}: \\
	Can be done efficiently by CuFFT (GPU) / FFTW (CPU) !
\end{itemize}
\end{frame}

@@

\section{Implementation \& results}
\begin{frame}{Time Complexity \& Work load balance}
The total computational cost of the method is
\begin{equation}
\underbrace{O(NP^3)}_{\text{Gaussian gridding}} + \underbrace{O(M^3 \log(M^3))}_{\text{FFT + iFFT}} + \underbrace{O(M^3)}_{\text{Scaling on k-space}} + \underbrace{O(N^2 p_{\infty}^3)}_{\text{Real space}}
\end{equation}
\textbf{Ewald parameter $\xi$ trades off between real space and k-space!}
\begin{itemize}
	\item Larger $\xi \rightarrow$ larger $M$, smaller $p_{\infty}$.
	\item Smaller $\xi \rightarrow$ smaller $M$, larger $p_{\infty}$.
\end{itemize}
How we choose the parameters:
\begin{itemize}
	\item \textbf{Balance the error} \\
	\item \textbf{Balance the time}
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Acceleration \& parallelization}
\begin{itemize}
	\item Compute $u^F$ (k-space) by FFT \\
	\begin{equation}
	\mathbf{u}^F (\mathbf{x}_m) = \frac{1}{V} \sum_{\mathbf{k} \neq 0} \mathbf{B}(\xi, \mathbf{k}) e^{-k^2/4\xi^2} \left(\sum_{n=1}^{N} \mathbf{f}_n e ^{i \mathbf{k} \cdot \mathbf{x}_n} \right)e ^{-i \mathbf{k} \cdot \mathbf{x}_m}
	\end{equation}
	is the combination of two steps of NuFFT (Non-uniform FFT).

	\textbf{Can be done efficiently by Gaussian Gridding \& FFT!}
	\begin{itemize}
		\item \textbf{Gaussian Gridding}: \\
		Compute $ \sum_{n=1}^N \mathbf{f}_n e^{-2 \xi^2 |\mathbf{x} - \mathbf{x}_n|_{\ast}^2 / \eta}$ \\
		Can be accelerated with Greengard's trick \cite{Greengard2004} and  OpenMP!
		\item \textbf{FFT}: \\
		Can be done efficiently by CuFFT (GPU) / FFTW (CPU) !
	\end{itemize}

	\item Accelerate $u^R$ (real space) by OpenMP 
\end{itemize}

\end{frame}

@@

\section{Implementation \& results}

\begin{frame}{Spectral convergence}
The three type of error versus the corresponding parameter, \\
all has \textbf{spectral convergence}!
\begin{figure}[H]\centering
	\includegraphics[width=.36\textwidth]{freq_error_vs_k}
	\includegraphics[width=.36\textwidth]{qudrature_error_vs_P}
	\includegraphics[width=.36\textwidth]{real_error_vs_r}
\end{figure}
\end{frame}
\begin{frame}{Time Complexity \& Work load balance}
The total computational cost of the method is
\begin{equation}
\underbrace{O(NP^3)}_{\text{Gaussian gridding}} + \underbrace{O(M^3 \log(M^3))}_{\text{FFT + iFFT}} + \underbrace{O(M^3)}_{\text{Scaling on k-space}} + \underbrace{O(N^2 p_{\infty}^3)}_{\text{Real space}} + \underbrace{O(N)}_{self}
\end{equation}
if no FFT acceleration, the cost is
\begin{equation}
\underbrace{O(N^2M^3)}_{k-space} + \underbrace{O(N^2 p_{\infty}^3)}_{\text{Real space}} + \underbrace{O(N)}_{self}
\end{equation}
\textbf{Ewald parameter $\xi$ trades off between real space and k-space!}
\begin{itemize}
	\item Larger $\xi \rightarrow$ larger $M$, smaller $p_{\infty}$.
	\item Smaller $\xi \rightarrow$ smaller $M$, larger $p_{\infty}$.
\end{itemize}
How we choose the parameters:
\begin{itemize}
	\item \textbf{Balance the error} \\
	\item \textbf{Balance the time}
\end{itemize}
\end{frame}
